---
title: "kable tables"
format: html
editor: visual
---

## kable table whatthe is that?

```{r}
#install.packages("kableExtra")
library(tidyverse) 
library(lterdatasampler) 
library(kableExtra)
```

create a summary table of mean maple seedling height cm\^2 by watershed and year

```{r}
hbr_summary <- hbr_maples |> 
  group_by(watershed, year) |> 
  summarise(mean_height = round(mean(stem_length, na.rm = TRUE), 1), 
            sd_height = round(sd(stem_length, na.rm = TRUE), 1))
```

there ar like a million ways to create tables in R that look good enough to publish in a paper or something that you want

use package "kableExtra"

make a nicer table! (uses html to make it look pretty)

use round function to keep sig figs in line... original data was only measured in tenths of a centimeter

```{r}
hbr_summary |> 
  kable(col.names = c("Watershed", "Year", "Mean Seedling Height (sq. cm)", "SD seedling height (sq. cm)")) |> 
  kable_styling(bootstrap_options = "striped") |> 
  column_spec(1, bold = TRUE, background = "purple") |> 
  add_header_above(c(" " = 2, "Seedling dimensions" = 2)) |> 
  scroll_box(height = 50, width = 200) #if you have a big table and want to save space 
```
